Model LF

### 2022-10-26 max_dp endogen stød.Rmd
Commit
Tilføjet elasticiteter

```{r}
S_model=LOAD_MODEL(modelText = S_model.txt)
```

@@

S_modelData$d_2007q4 = d_2007q4

@@

nl_g_bs56 = Shock_bs56$simulation$nl_g

yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

@@

nl_g_bs7 = Shock_bs7$simulation$nl_g

yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prod_bs7 = Shock_bs7$simulation$prod
```

@@

yk_ds_05 = Shock_5$simulation$yk_ds
emp_05 = Shock_5$simulation$emp
wage_ds_05= Shock_5$simulation$wage_ds
ur_ds_05 = Shock_5$simulation$ur_ds
pc_ds_05 = Shock_5$simulation$pc_ds
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
pconk_ds_05 = Shock_5$simulation$pconk_ds
komp_r_05 = Shock_5$simulation$komp_r
max_dp_05 = Shock_5$simulation$max_dp
nben_h_05 = Shock_5$simulation$nben_h
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
ik_05 = Shock_5$simulation$ik
wage_ds_t_05 = Shock_5$simulation$wage_ds_t
nben_h_un_05 = Shock_5$simulation$nben_h_un
nl_g_05 = Shock_5$simulation$nl_g
nsben_h_05 = Shock_5$simulation$nsben_h
dp_person_05 = Shock_5$simulation$dp_person
u_ds_05 = Shock_5$simulation$u_ds
shock_kuld_05 = Shock_5$simulation$shock_kuld

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld

@@

>>>>

## update txt
```{r}
S_model=LOAD_MODEL(modelText = S_model.txt)
```

@@

#S_modelData$d_2007q4 = d_2007q4

@@

nl_g_bs56 = Shock_bs56$simulation$nl_g
unemp_bs56 = Shock_bs56$simulation$unemp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

@@

nl_g_bs7 = Shock_bs7$simulation$nl_g
unemp_bs7 = Shock_bs7$simulation$unemp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prod_bs7 = Shock_bs7$simulation$prod
```

@@

yk_ds_05 = Shock_5$simulation$yk_ds
emp_05 = Shock_5$simulation$emp
wage_ds_05= Shock_5$simulation$wage_ds
ur_ds_05 = Shock_5$simulation$ur_ds
pc_ds_05 = Shock_5$simulation$pc_ds
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
pconk_ds_05 = Shock_5$simulation$pconk_ds
komp_r_05 = Shock_5$simulation$komp_r
max_dp_05 = Shock_5$simulation$max_dp
nben_h_05 = Shock_5$simulation$nben_h
yd_hk_ds_05 = Shock_5$simulation$yd_hk_ds
ik_05 = Shock_5$simulation$ik
wage_ds_t_05 = Shock_5$simulation$wage_ds_t
nben_h_un_05 = Shock_5$simulation$nben_h_un
nl_g_05 = Shock_5$simulation$nl_g
nsben_h_05 = Shock_5$simulation$nsben_h
dp_person_05 = Shock_5$simulation$dp_person
u_ds_05 = Shock_5$simulation$u_ds
shock_kuld_05 = Shock_5$simulation$shock_kuld
unemp_05 = Shock_5$simulation$unemp

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld
unemp_07 = Shock_7$simulation$unemp
```

@@

# Elasticiteter

## Micro elasticitet

Using 2.5% increase in the income insurance in 2020

**effect with full approach rate**

```{r}
pr_c_unemp=2.900/176.08443*100

e1= pr_c_unemp/2.5;e1
```

**Effect with Dørs approach rate**

We change the results of the approach effect to 650 instead of 1300

```{r}
pr_c_unemp= 2.250/176.08443*100

e2= pr_c_unemp/2.5;e2
```

**Effect without the approach rate**

```{r}
pr_c_unemp= 1.6/176.08443*100

e3= pr_c_unemp/2.5;e3
```

## Macro elasticitet

**Macro effect with productivity**

```{r}
change_unemp_pr_05= (unemp_05 - unemp_bs56)/unemp_bs56
change_dp_person_pr_05= (dp_person_05 - dp_person_bs56)/dp_person_bs56
```

```{r}
e3= change_unemp_pr_05/change_dp_person_pr_05;e3
```

**Macro effect without productivity**

```{r}
change_unemp_pr_07= (unemp_07 - unemp_bs7)/unemp_bs7
change_dp_person_pr_07= (dp_person_07 - dp_person_bs7)/dp_person_bs7
```

```{r}
e3= change_unemp_pr_07/change_dp_person_pr_07;e3
```
